A Spiking Independent Accumulator Model for Winner-Take-All Computation

### 2017-04-17 doc/paper/paper.tex
Address some of the review comments.

@@

In contrast, the IA network is better suited for situations where a discrete sequence of decisions is required.
After selecting a winner, the model's decision will persist due to self-excitation, even in the absence of input.
Thus, after making a decision, it is necessary to reset the model by inhibiting the winning accumulator.
This limits how quickly successive decisions can be made and reduces the ability to react to changing inputs.
However, once a decision is made, the network provides a stable output.

Both models might produce a transient response that may be interpreted as a decision, which can make the detection of decisions problematic.
This is of special relevance when incorporating the networks into larger cognitive models.
For the LCA network, the transient behaviour is inherent to its design; there will always be an initial rise of all state variables (that receive input) before the mutual inhibition grows strong enough to push them back to zero.
In the IA network, however, such transient responses may be avoided by choosing appropriate $\tau_1$ and $\vartheta$.

>>>>

Note that the layer 2 decoded output of a single choice shows more variance in the IA network (Fig.~\ref{fig:indacc}), but the separation of the output for different choices is more relevant in interpreting the output.

@@

In contrast, the IA network is better suited for situations where a discrete sequence of decisions is required.
After selecting a winner, the model's decision will persist due to self-excitation, even in the absence of input.
Thus, after making a decision, it is necessary to reset the model by inhibiting the winning accumulator.
This limits how quickly successive decisions can be made and reduces the ability to react to changing inputs.
However, once a decision is made, the network provides a stable output.
As an example, we intend to use the IA network in a free recall memory model where a clear response needs to be selected.
A non-correct response in this case might still be a valid response in the context of this task and could be better than no response at all.

Both models might produce a transient response that may be interpreted as a decision, which can make the detection of decisions problematic.
This is of special relevance when incorporating the networks into larger cognitive models.
For the LCA network, the transient behaviour is inherent to its design; there will always be an initial rise of all state variables (that receive input) before the mutual inhibition grows strong enough to push them back to zero.
In the IA network, however, such transient responses may be avoided by choosing appropriate $\tau_1$ and $\vartheta$.
It should be noted that other recurrently connected readout mechanisms with pooled inhibition have been proposed for at least the two choice case~\cite<e.g.>{lo2006} that produce outputs somewhat comparable to the IA network.
